### 2021-06-04 paper/report.tex
Add preliminary model graphs.
Add a couple of paragraphs.

\clearpage

Since early 2020, the CoViD-19 pandemic has presented an enormous challenge to humanity on many dimensions. The development of highly effective vaccines holds the promise of containment in the medium term. However, most countries find themselves many months---and often years---away from reaching vaccination-induced herd immunity.\comment[id=HM]{Cite some paper on herd immunity, maybe vaccine data} In the meantime, it is of utmost importance to employ an effective mix of strategies for containing the virus. The most frequent initial response was a set of non-pharmaceutical interventions (NPIs) to reduce contacts between individuals. While this has allowed some countries to sustain equilibria with very low infection numbers\comment[id=HM]{Cite Priesemann paper or other}, most have seen large ups and downs in their infection rates. Containment measures have become increasingly diverse and included testing, more nuanced NPIs, and contact tracing. In quantitative terms, neither these policies' effect nor the influence of seasonal patterns or more infectious virus strains are well understood. This paper develops a model incorporating all these influences. The framework allows to combines a wide variety of data in a timely fashion and to predict the effects of various interventions. We apply the model to Germany and show that rapid testing had the largest impact on the reduction in infections by XXX\% during the A weeks between X April and Y May.\comment[id=HM]{insert something useful}

At the core of our agent-based model are physical contacts between heterogeneous agents (See Figure~\ref{fig:model_graph}a).\footnote{We provide a detailed comparison to other approaches in \ref{sec:literature_review}, where we also review other approaches. The model most closely related to ours is described in \citet{Hinch2020}.} Each contact between an infectious indvidual and somebody susceptible to the disease bears the risk of transmitting the virus. Contacts occur in the household, at work, at school, or in other settings (leisure activities, grocery shopping, medical appointments, etc.).\comment[id=HM]{Systemic relevance of work?} Some contacts recur regularly, others occur at random. Random contacts are typically assortative in age and geographical location. Empirical applications can take the population structure from census data and the types and frequency of contacts from diary data measuring contacts before the pandemic \citep[e.g.][]{Mossong2008}.\comment[id=HM]{cite other stuff, too?} The dimensions are chosen so that the most common NPIs can be modelled in great detail by reducing the number of contacts in a particular setting or the risk of transmitting the disease for a type of contact. For example, a mandate to work from home will reduce the number of work contacts to zero for a fraction of the working population. Schools and daycare can be closed entirely, operate at reduced capacity including an alternating schedule, or implement mitigation measures like masking requirements or air filters.\comment[id=HM]{cite \url{https://science.sciencemag.org/content/early/2021/04/28/science.abh2939}} Curfews may reduce the number of contacts in non-work/non-school settings. In any setting, measures like masking requirements would reduce the probability of infection associated with a contact.

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/model_detailed.png}
        \caption{{\small Model description}}
        \label{fig:model_graph}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/disease_progression.png}
        \caption{Disease progression}
        \label{fig:disease_progression}
    \end{subfigure}

@@

        % \includegraphics[width=\textwidth]{../figures/model_detailed.png}
        \caption{{\small PCR and antigen tests}}
        \label{fig:pcr_antigen_tests}
    \end{subfigure}
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

@@

Susceptibility to contracting CoViD-19 is dependent on age and so is the progression of the disease. We differentiate between an inital period of infection without being infectious or showing symptoms, being infectious (presymptomatic or asymptomatic), showing symptoms, requiring intensive care, and recovery or death. The probabilities of transitioning between these states depend on age; their duration is random within intervals calibrated to medical literature.\comment[id=HM]{Cite}. Conditional on the type of contact, infectiousness independent of ages.\comment[id=HM]{Cite current Drosten paper}

@@

Identification

Modelling a population of agents according to actual demographic characterists means that we can use a wide array of data to estimate the model parameters. Mobility data is used to inform reductions in work and social contacts.\comment[id=HM]{check} School and daycare policies can be incorporated directly from official directives. Infection rates by age and geographical region are matched to officially recorded numbers, so is the prevalence of virus strains. In order to translate simulated cases in our model to officially recorded cases, we use the model depicted in Figure~\ref{fig:model_for_official_cases}.

Simulated data have very similar structure to data that is used for regression analyses. Can use as further plausbility check.

\paragraph{Example: Germany}
\begin{itemize}
    \item Good first response, relatively lax (no curfew, few business closures, ... )
    \item Then relaxed over the summer at low incidence rates
    \item Cross-country mobility planted the seeds for fall wave
    \item We start our analysis at this point because modelling undetected cases would require a very different approach than in spting
\end{itemize}

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/work_multiplier_since_sep}

        Stringency index + multipliers

@@

        \includegraphics[width=\textwidth]{../figures/results/figures/data/share_receiving_vaccination_per_day}

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
        \caption{{\small Recorded cases: 2021 scenarios}}
        \label{fig:full_new_known_case_cropped}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
        \caption{{\small Total cases: 2021 scenarios}}
        \label{fig:full_newly_infected_cropped}
    \end{subfigure}
    \vskip3ex

>>>>

% \clearpage

Since early 2020, the CoViD-19 pandemic has presented an enormous challenge to humanity on many dimensions. The development of highly effective vaccines holds the promise of containment in the medium term. However, most countries find themselves many months---and often years---away from reaching vaccination-induced herd immunity.\comment[id=HM]{Cite some paper on herd immunity, maybe vaccine data} In the meantime, it is of utmost importance to employ an effective mix of strategies for containing the virus. The most frequent initial response was a set of non-pharmaceutical interventions (NPIs) to reduce contacts between individuals. While this has allowed some countries to sustain equilibria with very low infection numbers\comment[id=HM]{Cite Priesemann paper or other}, most have seen large ups and downs in their infection rates. Containment measures have become increasingly diverse and included testing, more nuanced NPIs, and contact tracing. Neither these policies' effect nor the influence of seasonal patterns or more infectious virus strains are well understood in quantitative terms. This paper develops a model incorporating all these factors. The framework allows to combine a wide variety of data in a timely fashion, making it useful to predict the effects of various interventions. We apply the model to Germany and show that rapid testing had the largest impact on the reduction in infections by XXX\% during the A weeks between X April and Y May.\comment[id=HM]{insert some useful numbers}

At the core of our agent-based model are physical contacts between heterogeneous agents (Figure~\ref{fig:broad_model_description}).\footnote{We provide a detailed comparison to other approaches in \ref{sec:literature_review}. The model most closely related to ours is described in \citet{Hinch2020}.} Each contact between an infectious indvidual and somebody susceptible to the disease bears the risk of transmitting the virus. Contacts occur in the household, at work, at school, or in other settings (leisure activities, grocery shopping, medical appointments, etc.).\comment[id=HM]{Systemic relevance of work?} Some contacts recur regularly, others occur at random. Random contacts are typically assortative in age and geographical location. Empirical applications can take the population structure from census data and the types and frequency of contacts from diary data measuring contacts before the pandemic \citep[e.g.][]{Mossong2008}.\comment[id=HM]{cite other stuff, too?} The dimensions are chosen so that the most common NPIs can be modelled in great detail by reducing the number of contacts in a particular setting or the risk of transmitting the disease for a type of contact. For example, a mandate to work from home will reduce the number of work contacts to zero for a fraction of the working population. Schools and daycare can be closed entirely, operate at reduced capacity including an alternating schedule, or implement mitigation measures like masking requirements or air filters.\comment[id=HM]{cite \url{https://science.sciencemag.org/content/early/2021/04/28/science.abh2939}} Curfews may reduce the number of contacts in non-work/non-school settings. In any setting, measures like masking requirements would reduce the probability of infection associated with a contact.

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/model-graph-top-left}
        \caption{{\small Model description}}
        \label{fig:broad_model_description}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/model-graph-top-right}
        \caption{Disease progression}
        \label{fig:disease_progression}
    \end{subfigure}

@@

        \includegraphics[width=\textwidth]{../figures/model-graph-bottom-left}
        \caption{{\small PCR and antigen tests}}
        \label{fig:pcr_antigen_tests}
    \end{subfigure}
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

@@

Susceptibility to contracting the SARS-CoV-2 virus is dependent on age; so is the progression of a possible infection. We differentiate between an inital period of infection without being infectious or showing symptoms, being infectious (presymptomatic or asymptomatic), showing symptoms, requiring intensive care, and recovery or death. The probabilities of transitioning between these states depend on age; their duration is random within intervals calibrated to medical literature.\comment[id=HM]{Cite}. Conditional on the type of contact, infectiousness independent of ages.\comment[id=HM]{Cite current Drosten paper}

@@

Modelling a population of agents according to actual demographic characterists means that we can use a wide array of data to identify and estimate the model's many parameters.\footnote{See section S.X of the supplementary materials for an overview.}\comment[id=HM]{Need to make a list including symbols, maybe you can fetch the parameters from the model and then we brainstorm re notation?} Mobility data is used to model the reductions in work contacts. School and daycare policies are incorporated directly from official directives. Infection rates by age and geographical region are estimated to match to officially recorded numbers; so is the prevalence of virus strains. In order to translate simulated cases in our model to officially recorded cases, we use the model depicted in Figure~\ref{fig:model_for_official_cases}. \comment[id=HM]{Add a sentence.} A further advantage is that the simulated data have a structure that resembles datasets used for regression models, which allows additional plausibility checks by re-running the same models on the model-generated data.\comment[id=HM]{Only keep if we actually do something like that.}

We apply this model to Germany. In March and April 2020, the country broke the first wave of the pandemic fairly quickly. Between mid-May and mid-September, daily new infections were below 20 per Million and day.\comment[id=HM]{Cite our world in data} We start our analysis in mid-September for two reasons. First, we do not include the first wave because the environment was very different (e.g., aggregate PCR test capacity was much lower and we would require a very different model for calculating the share of known cases) and some data was not recorded yet.\comment[id=HM]{True?}. Many cases during the summer of 2020 were traced to international travellers; our model is not very helpful in explaining this.

In late summer and early fall, restrictions were few. A distance of 1.5m had to be kept and masking requirements were enforced in public locations.\comment[id=HM]{pls double-check, add if I am missing important stuff}. Figure~\ref{fig:pandemic_drivers_model_fit} describes the background for our analysis. Figure~\ref{fig:stringency_index} Important to remember that multipliers are relative to that period

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/work_multiplier_since_sep}
        Stringency index + multipliers

@@

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
        \caption{{\small Recorded cases: 2021 scenarios}}
        \label{fig:full_new_known_case_cropped}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
        \caption{{\small Total cases: 2021 scenarios}}
        \label{fig:full_newly_infected_cropped}
    \end{subfigure}
